Criticisms of the IHME COVID-19 model

### 2020-05-07 text/20/ihme-covid-model.Rmd
Added bias-catalog

@@

>>>>

Mortality Modeling FAQ. Available in [html format](https://covid-19.tacc.utexas.edu/mortality-projection-faq/).

+ This is a different group (University of Texas at Austin) that is using a similar approach for modeling. It is interesting to see a common justification from both groups for their atheoretical approach.

Social Distancing: Data Models for a Model Response to an Outbreak. Available in [html format](https://sph.umich.edu/news/2020posts/data-models-for-a-model-response-to-an-outbreak.html).

+ This is a question and answer session with Dr. Peter Song of the University of Michigan Department of Public Health. Dr. Song has fit some sophisticated SEIR models that can predict the impact of social distancing on the spread of COVID-19 cases. It is a nice summary, with enough details to let you know what the work involves without getting too technical.

@@

Ayoub HH, Chemaitelly H, Mumtaz GR, Seedat S, Awad SF, Makhoul M, Abu-Raddad LJ. Characterizing key attributes of the epidemiology of COVID-19 in China: Model-based estimations. Preprint published in Medrxiv, 2020-04-11. Available in [pdf format](https://www.medrxiv.org/content/10.1101/2020.04.08.20058214v1.full.pdf).

+ This article fits an SEIR model to the Chinese COVID outbreak. It stratifies by age and outlines the differential equations in great clarity.

Wang L, Wang G, Gao L, Li X, Yu S, Kim M, Wang Y, Gu Z. Spatiotemporal Dynamics, Nowcasting and Forecasting of COVID-19 in the United States. Preprint published in Arxiv, 2020-04-30. Available in [pdf format](https://arxiv.org/pdf/2004.14103.pdf).

+ This article fits an SEIR model to individual counties in the United States with a large number of county specific covariates. The model produces a [nice dashboard](https://covid19.stat.iastate.edu/).
